%----------------------------------------------------------------------------------------
%	CATEGORIZATION BY GOALS
%----------------------------------------------------------------------------------------

\section{Categorization by Goals} % Major section

Machine learning algorithms can also be classified by the output or end goal of the algorithm. When the input is mapped to a discrete set of classes, the algorithm is said to perform ``classification.'' In such cases as the class set is binary, the algorithm is said to perform ``decision.'' When the input is mapped to a continuous output, the algorithm is said to perform ``regression.'' When the input is grouped together into unlabeled classes, the algorithm is said to perform ``clustering.''

%------------------------------------------------

\subsection{Classification and Decision} % Sub-section

Machine algorithms which perform classification (``classifiers'') and decision (``deciders'') are useful for taking input and matching it to a particular class within a set of classes. By definition, the output of a classifier is a discrete value. Classification is often performed with supervised learning, where the machine is provided a training set of example inputs and their associated classes, and the algorithm then produces a decision boundary between each class to predict the classification of future inputs. An example of a decider (classifying input between two possible classes) would be a machine designed to predict whether a tumor is malignant or benign. The machine would be provided a training set of tumor data, including size, location, and class (malignant or benign). The machine would then be tasked with classifying other tumors based on their size and location. \cite{website:ng}

%------------------------------------------------

\subsection{Regression} % Sub-sub-section

Machine algorithms which perform regression are useful for taking input and predicting an output. The output of a regression algorithm is a continuous value. Regression is often performed with supervised learning, where the machine is provided a training set of examples, and the algorithm generates a closest fit function to predict the output value of future inputs. The example in the previous section of a machine with predicts housing prices by size and location would be an example of regression.

%------------------------------------------------

\subsection{Clustering} % Sub-sub-section

Machine algorithms which perform clustering are useful for exploring data and finding hidden structure within large sets of data. The example in the previous section of a machine identifying families of flowers is an example of clustering.

%------------------------------------------------